Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-12 code/data-preparation.Rmd
updated work relating to trying to determine the issue with the number of observations in the training data

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(stringr)
```

@@

@@

```{r}
bullet_train <- 
  bullet_train_raw %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-BQ-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-BQ-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
```

>>>>

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
```

@@

Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data:

```{r}
bullet_train_raw_expanded <-
  bullet_train_raw %>%
  separate(land_id1,
           sep = "-",
           into = c("study1", "barrel1", "bullet1", "land1")) %>%
  separate(land_id2,
           sep = "-",
           into = c("study2", "barrel2", "bullet2", "land2"))
```

The number of comparisons within the two studies are included below:

```{r}
table(
  bullet_train_raw_expanded$study1,
  bullet_train_raw_expanded$study2
)
```

The dimension of the data once the observations with tank rash (`flag != FALSE`) are removed:

```{r}
bullet_train_raw %>% filter(flag == FALSE) %>% dim()
```

The number of observations in the random forest `rtrees` (note that they do not match the number of rows in the above dataset):

```{r}
length(bulletxtrctr::rtrees$predicted)
```

@@

```{r}
bullet_train <- 
  bullet_train_raw %>%
  filter(flag == FALSE) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
```
